Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-20 paper/ms.tex
final corrections on ms

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. {\bf We use this approach to avoid the uncertainties associated
  to the estimation of \ly luminosities in each halo.} Our analysis
shows that the clustering and number density information are
insufficient to impose a tight constraint on the {\bf   occupation}
fraction. On the other hand, the minimum mass and maximum mass can be
constrained to the range $M_{\rm  max}<10^{12}$\hMsun and
$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that the consistent models have a narrow mass range, $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
with a majority in the range $\Delta M<0.5$ dex. {\bf These results
  broadly reproduce some constraints   already presented in the
  literature. However, the wide range of  values for the escape
  fraction and the narrow mass ranges are novel results from
  the approach presented here}. We conclude that achieving a constraint on the
occupation fraction for LAEs at $z=3.1$ will require observations on
larger fields to reduced cosmic variance and robust physical models
for the connection between dark matter, star formation and the escape
of \ly radiation. That kind of modeling should also be able to provide
a plausible explanation for the narrow mass range derived here for the
halos hosting LAEs at $z=3.1$. 
\end{abstract}

@@

Our method first populates DM halos in cosmological simulations with
LAEs. We only consider whether a DM can host a detectable LAE or not
without predicting a \ly  luminosity. This bypasses all the physical
uncertainties involved in the estimation of observed \ly luminosities.
Once we have the mock LAE catalogs, we compare them against
observations in terms of the  statistics on the number density
distribution derived from the observations over the 12 fields of
\cite{Yamada2012}. We also use measurements of the angular
correlation function to improve these constraints. This method allows
us to constraint the preferred mass range and occupation fraction of DM
halos hosting LAEs.

This \documentname is structured as follows. In the next section we present
the simulation and the model used to produce the mock catalogs. We
also list the criteria used to compare the mocks against
observations. In \S \ref{sec:results} we present the main results for
the halo mass and occupation fraction. We continue with a discussion
of these results under the light of other observational and
theoretical results. Finally, we present our conclusions in \S
\ref{sec:conclusions}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass. Each line
  represents one of the $210$ volumes of dimensions $46\times 35\times
  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
  gray band represents the range of surface densities observed for
  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
  line the observational results by \citet{Ouchi2008}.}
\end{center} 
\end{figure*}

The primary observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
an observed equivalent width, in the observer frame, larger than $190$
\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
sub-fields,  this corresponds to average surface number density of
$0.24\pm 0.01$ arcmin$^{-2}$.

@@

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. In the case of
  \cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
  is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
  the general fields in \cite{Yamada2012}}

\subsection{The adequacy of including SSA22 as an observational benchmark}

@@

{\bf All the other sub-fields in SSA22 are average. They have a similar
  number density as other blank fields. The left panel in Figure
  \ref{fig:halos} shows the integrated distribution of LAEs number
  density in all the fields reported in  \cite{Yamada2012}. It is
  evident that there is only one sub-field  that stands out as an
  outlier in the distribution (it corresponds to  the densest field in
  SSA22). All the other fields form a continuous  distribution in
  number density.}

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. We do not require the presence of such field to judge a mock
  distribution as successful. The statistical test we perform to
  compare mock distributions   against   observations does not require
  such a perfect match. }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs in a mock
  survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern.}
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
must keep in mind that the physical interpretation of the occupation
fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
forming galaxy in a halo and its detectability as a LAE.

{\bf We recall that we do not perform a explicit modeling for LAE
detectability. Our model does not assign a luminosity or escape
fraction for each LAE. We are interested in constraining the halo
mass range hosting detectable LAEs commonly used in photometric
narrow-band surveys. We also want to explore a wide range of
possible masses for the host halos without any strong theoretical
prejudice regarding the details of star formation in high-redshift
galaxies. }

@@

Next we construct mock surveys by making groups of $12$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping of the $12$
mock fields into a mock catalog is done in two different ways. The
first is called {\texttt{match}}, it follows the clustering of the
observational fields. From the $12$ mock fields, $7$ are constructed
from contiguous fields in the simulation to mimic the SSA22 region,
$3$ are also contiguous between them but not to the first $7$ fields
to mimic the SXDS fields and finally $2$ non-contiguous fields to
imitate the SDF and GOODS-North field.   The second way to group the
mock fields is called {\texttt{random}}, whereby all the $12$ fields
are selected in such a way as to avoid that any two volumes are
contiguous. In this \documentname we only report the results obtained
by the {\texttt{match}} method and mention explicitly differences
observed with the {\texttt{random}} selection.

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
one out of the $15$ different mock surveys that are constructed for
each model. We note that we only use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

We make a thorough exploration of the parameter space for the models
${\mathcal M}$ where $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
takes values in the same range as $\log_{10}M_{\rm min}$ only with a
displacement of $0.1$ dex in the whole range. The occupation fraction
$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regularly
spaced by $0.1$. In total the number of different models ${\mathcal
  M}$ that are explored is $30 \times 30 \times 10 = 9000$.

@@

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parameters. The fit is done
using a least square minimization procedure. For each mock field we
obtain a covariance matrix that gives us the uncertainty in the
parameters $\beta$ and $\theta_0$. {\bf We consider that a mock field is
consistent with observations if the two parameters $\beta$ and
$\theta_0$ are equal within a $1$-$\sigma$ range.}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of mock surveys
  compatible with observations. Only regions in the parameter space with
  at least one consistent mock survey are
  included. \label{fig:landscape}}      
\end{figure*}

The main purpose of this section is to show how different
observational constraints narrow down the parameters space of allowed
models. Each sub-section presents the effect of adding a new piece of 
observational or statistical evidence.

@@

This plot allows us to understand why only a specific range of
models ${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models with
a minimum mass $M_{\rm min}>10^{12}$\hMsun always have a
surface number density lower than the observational constrain, making
them incompatible with observations; there are simply too few halos compared to observed
LAEs. The opposite is true in models with $M_{\rm
  min}<10^{11.0}$\hMsun that have a surface number density larger
observations. In those cases the maximum mass $M_{\rm max}$ and the
occupation fraction $f_{\rm occ}<1.0$  can be tuned in order to lower
the halo number density to match observations.

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed minimum mass there is an scatter of $0.3-0.6$ dex
in the number density abundance, which is of the same order of
magnitude as the scatter in the observational data.  As a consequence, the variation in
the number density in mocks for models with the same mass range and occupation
fraction can be by factors of $\sim 2-5$.  This scatter induced by
cosmic variance is naturally included in the mock construction
process. This variance will explain that very different models can be
made compatible with observations.

@@

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test
between the mocks and observations yields values of $P>0.05$ for at
least one mock survey in each model. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution.

In total, there are between $550$ to $600$ models out of the original
$9000$ models that have at least one mock survey consistent with
observations. By inspection of Figure \ref{fig:landscape} we see that
the halo number abundance is able to constraint the minimum mass
$M_{\rm min}$ to a narrow range, while $M_{\rm max}$ and $f_{\rm occ}$
remain largely unconstrained.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. Only the results
  for the {\texttt{match}} method are shown.
  \label{fig:restriction_mock}}  
\end{figure*}

@@

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$. With this constraint the number of consistent
models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
corresponds to the regions in the parameter space in
Figure \ref{fig:landscape} that already had a low number of 
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} we see that the favored occupation
fraction  still remain unconstrained $0\leq f_{\rm  occ}\leq 1.0$.

@@

The left panel of the figure \ref{fig:correlation_parameters} shows the results for the
best estimates of $\theta_{0}$-$\beta$  used in the ACF
parameterization.  Blue circles with error bars represent the results
from the mocks and the horizontal line the observational results of
\cite{Ouchi2010} over a field with average number density where the
$\beta$ parameter was fixed in the fit. From this Figure we observe
that there are models with too large values of $\theta_0$ and $\beta$
that can be ruled out as inconsistent with the angular correlation
function.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
remaining consistent models in the planes $M_{\rm min}$-$M_{\rm
  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
observations if there is a $1$-$\sigma$ overlap between both the
correlation length $\theta_0$ and the exponent $\beta$.  We find that
we end up with $40$ models consistent with the ACF constraints.

@@

From this comparison we conclude that clustering information can
constrain the values of $M_{\rm max}$, but not the occupation
fraction.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
\end{center}
\caption{Left panel. Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
bars in the theoretical data correspond to the quadratic average of
the fitting uncertainties for each mock survey. Right panel. Values of $\theta_{0}$  and $\log_{10}(M_{min}/M_{\odot} h^{-1})$. Blue and green point represents the models where  $\log_{10}(M_{max}/M_{\odot} h^{-1})<12.0$ and  $\log_{10}(M_{min}/M_{\odot} h^{-1})>12.0$ respectively. .  The horizontal gray band represents the observational contraints on $theta_{0}$ stablished by   \citet{Ouchi2008,Ouchi2010}. Green points has been displaced by $0.01dex$ of its original value to avoid overlapping between blue and green points.} \label{fig:correlation_parameters}  
\end{figure*}

@@

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. These 
  models they have another particular feature: their minimum mass is
  exactly $M_{\rm min}=10^{10.9}\hMsun$ m and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$ close to $1.0$
  (instead of the observational value of $0.8$) and $\theta_0$ on the
  range of $13^{\prime}$ (the mean observational value is close to
  $8^{\prime}$) but are considered
  consistent because their large error bars barely overlap with the
  observational expectation (see figure \ref{fig:correlation_parameters})  .  Because these models are
  are barely compatible with observations and are a minority of the
  consistent models, we exclude them from the rest of the discussion.}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. The observational data for the ACF
  corresponds to 
  \citet{Ouchi2008,Ouchi2010}.   
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

\subsection{Two relevant features in the preferred models}
There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. {\bf We use this approach to avoid the uncertainties associated
  to the estimation of \ly luminosities in each halo.} Our analysis
shows that the clustering and number density information are
insufficient to impose a tight constraint on the {\bf   occupation}
fraction. On the other hand, the minimum mass and maximum mass can be
constrained to the range $M_{\rm  max}<10^{12}$\hMsun\ and
$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$. We also find
that the consistent models have a narrow mass range, $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
with a majority in the range $\Delta M<0.5$ dex. {\bf These results
  broadly reproduce some constraints   already presented in the
  literature. However, the wide range of values for the occupation
  fraction and the narrow mass range $\Delta M$ are novel results from
  the approach presented here}. We conclude that achieving a constraint on the
occupation fraction for LAEs at $z=3.1$ will require observations on
larger fields to reduced cosmic variance and robust physical models
for the connection between dark matter, star formation and the escape
of \ly radiation. That kind of modeling should also be able to provide
a plausible explanation for the narrow mass range derived here for the
halos hosting LAEs at $z=3.1$. 
\end{abstract}

@@

The method we use here firstly populates DM halos in cosmological
simulations with LAEs. We only consider whether a DM can host a
detectable LAE or not without predicting a \ly  luminosity. This
bypasses all the physical uncertainties involved in the estimation of
observed \ly luminosities. Once we have the halos hosting a LAE, we
build mock surveys following the geometry of the observed fields by
\cite{Yamada2012}. This allows us to take explicitly into account the
effect of cosmic variance. We used this mock surveys to compared them
against observations in terms of the number density distribution and
the angular correlation function. This allows us to constraint the
preferred mass range and occupation fraction of DM halos hosting LAEs.

This \documentname is structured as follows. In the next section we present
the simulation and the model used to produce the mock catalogs. We
also list the criteria used to compare the mocks against
observations. In \S \ref{sec:results} we present the main results for
the halo mass and occupation fraction. We continue in \S
\ref{sec:discussion} with a discussion under the light of other
constraints already presented in the literature and theoretical
considerations of galaxy formation studies. Finally, we present our
conclusions in \S \ref{sec:conclusions}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Cumulative distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass. Each line
  represents one of the $210$ volumes of dimensions $46\times 35\times
  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
  gray band represents the range of surface densities observed for
  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
  line the observational results by \citet{Ouchi2008}.}
\end{center} 
\end{figure*}

The primary observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
an observed equivalent width, in the observer frame, larger than $190$
\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
sub-fields,  this corresponds to an average surface number density of
$0.24\pm 0.01$ arcmin$^{-2}$.

@@

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. In the case of
  \cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
  is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
  the general fields in \cite{Yamada2012}. In spite of these
  differences \cite{Ouchi2008} provides the most similar conditions
  to \cite{Yamada2012}.}

\subsubsection{The adequacy of including SSA22 as an observational benchmark}

@@

{\bf All the other sub-fields in SSA22 are average. They have a similar
  number density as other blank fields. The left panel in Figure
  \ref{fig:halos} shows the integrated distribution of LAEs number
  density in all the fields reported in  \cite{Yamada2012}. It is
  evident that there is only one sub-field  that stands out as an
  outlier in the distribution, corresponding to  the densest field in
  SSA22. All the other fields form a continuous  distribution in
  number density.}

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. For this reason we do not require the presence of a very
  dense field such as SSA22-1 to judge a mock distribution as
  successful. The statistical test we use o compare mock
  distributions against observations does not require such a perfect
  match. }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Example of the spatial distribution of a LAEs in a mock
  survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$. The large panel shows $7$ mock
  fields together mimicking the geometry of the SSA22 region. The
  intermediate panel shows $3$ mock fields corresponding to the SXDS
  region. The lower panels represent the SDF and GOODS-North
  fields. The same model has another 14 associated mock surveys build
  from different regions in the simulation, but constructed following
  the same pattern.} 
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range ($M_{\rm min}< M_{\rm h} < M_{\rm max}$) where LAEs reside
and the fraction ($f_{\rm occ}$) of such halos that host a detectable
LAE. The reader must keep in mind that the physical interpretation of
the occupation fraction $f_{\rm occ}$ convolves two phenomena: the
actual presence of a star forming galaxy in a halo and its
detectability as a LAE.

{\bf We recall that we do not perform a explicit modeling for LAE
detectability. Our model does not assign a luminosity or escape
fraction for each LAE. We are interested in constraining the halo
mass range hosting detectable LAEs commonly used in photometric
narrow-band surveys. We want to explore a wide range of
possible masses for the host halos without any strong theoretical
prejudice regarding the details of star formation in high-redshift
galaxies. }

@@

Next we construct mock surveys by making groups of $12$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping of the $12$
mock fields into a mock catalog is done in two different ways. The
first is called {\texttt{match}} because it follows the clustering of the
observational fields. From the $12$ mock fields, $7$ are constructed
from contiguous fields in the simulation to mimic the SSA22 region,
$3$ are also contiguous between them but not to the first $7$ fields
to mimic the SXDS fields and finally $2$ non-contiguous fields to
imitate the SDF and GOODS-North field.   The second way to group the
mock fields is called {\texttt{random}}, whereby all the $12$ fields
are selected in such a way as to avoid that any two volumes are
contiguous. In this \documentname we only report the results obtained
by the {\texttt{match}} method since we do not find any significant
difference with respect to the {\texttt{random}} method.

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{10.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
one out of the $15$ different mock surveys that are constructed for
each model. We note that we only use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

We make a thorough exploration of the parameter space for the models
${\mathcal M}$ where $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
to $12.9$ with an even spacing of $0.1$ dex, $\log_{10} M_{\rm max}$
takes values in the same range as $\log_{10}M_{\rm min}$ with a
displacement of $0.1$ dex in the whole range. The occupation fraction
$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regularly
spaced by $0.1$. In total the number of different models ${\mathcal
  M}$ that are explored is $30 \times 30 \times 10 = 9000$.

@@

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parameters. The fit is done
using a least square minimization procedure. For each mock field we
obtain a covariance matrix that gives us the uncertainty in the
parameters $\beta$ and $\theta_0$. {\bf We consider that a mock field is
consistent with observations if the two parameters $\beta$ and
$\theta_0$ are equal within a $1$-$\sigma$ range. We perform this
comparison only with the fields constructed using the {\texttt{match}}
method.}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
    occ}$ (right) planes for all models consistent with the
  observational number density (KS test values
  $P>0.05$.) The color code corresponds to the number of mock surveys
  compatible with observations. Only regions in the parameter space
  with at least one consistent mock survey are
  shown. \label{fig:landscape}}      
\end{figure*}

The main purpose of this section is to show how the different
observational constraints narrow down the parameters space of allowed
models. Each sub-section presents the effect of adding a new piece of 
observational or statistical evidence.

@@

This plot allows us to understand why only a specific range of
models ${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models with
a minimum mass $M_{\rm min}>10^{12}$\hMsun always have a
surface number density lower than the observational constrain, making
them incompatible with observations; there are simply too few halos
compared to observed LAEs. The opposite is true in models with $M_{\rm
  min}<10^{11.0}$\hMsun, which have a surface number density larger
observations. In those cases the maximum mass $M_{\rm max}$ and the
occupation fraction $f_{\rm occ}<1.0$  can be tuned in order to lower
the halo number density to match observations.

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed minimum mass there is an scatter of $0.3-0.6$ dex
in the number density abundance, which is of the same order of
magnitude as the scatter in the observational data.  As a consequence,
the variation in the number density in mocks for models with the same
mass range and occupation fraction can be by factors of $\sim 2-5$.
This scatter induced by cosmic variance is naturally included in the
mock construction process.

@@

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test
between the mocks and observations yields values of $P>0.05$ for at
least one mock survey.

There are between $550$ to $600$ models out of the original
$9000$ models that have at least one mock survey consistent with
observations. By inspection of Figure \ref{fig:landscape} we see that
the halo number abundance is able to constraint the minimum mass
$M_{\rm min}$ to a narrow range, while $M_{\rm max}$ and $f_{\rm occ}$
remain largely unconstrained.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_mass_mock.pdf} 
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_f_occ_mock.pdf}
\end{center}  
\caption{Favored regions in parameter space when we impose the
  condition of having all the mock surveys consistent with the
  observed number density distribution. Only the results for the
  {\texttt{match}} method are shown. \label{fig:restriction_mock}}  
\end{figure*}

@@

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}$-$M_{\rm max}$ and $M_{\rm
  min}$-$f_{\rm occ}$. With this constraint the number of consistent
models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
corresponds to the regions in the parameter space in
Figure \ref{fig:landscape} that already had a low number of 
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} we see that the favored occupation
fraction  still remain unconstrained $0\leq f_{\rm  occ}\leq 1.0$.

@@

The left panel in Figure \ref{fig:correlation_parameters} shows the
results for the best estimates of $\theta_{0}$-$\beta$  used in the
ACF parameterization on the best models previously selected.  Blue
circles with error bars represent the results from the mocks and the
horizontal line the observational results of \cite{Ouchi2008} over a
field with average number density where the $\beta$ parameter was
fixed in the fit. From this Figure we observe that there are models
with too large values of $\theta_0$ and/or $\beta$ that can be ruled
out as inconsistent.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
remaining consistent models in the planes $M_{\rm min}$-$M_{\rm
  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
observations if there is a $1$-$\sigma$ overlap between both the
correlation length $\theta_0$ and the exponent $\beta$.  We find that
we end up with $40$ models consistent with the ACF constraints.  This
is a reduction of a factor of $\sim 2$ with respect to the number of
models consistent with the number density distribution.

@@

From this comparison we conclude that clustering information can
constrain the values of $M_{\rm max}$. We emphasize that the
occupation fraction continues to be unconstrained.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
\end{center}
\caption{Left panel. Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
bars in the theoretical data correspond to the quadratic average of
the fitting uncertainties for each mock survey. Right panel. Values of
$\theta_{0}$  and $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})$. Blue and
green point represents the models where  $\log_{10}(M_{\rm max}/M_{\odot}
h^{-1})<12.0$ and  $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})>12.0$
respectively. .  The horizontal gray band represents the observational
constraints on $theta_{0}$ established by
\citet{Ouchi2008,Ouchi2010}. Green points has been displaced by
$0.01$ dex of its original value to avoid overlapping between blue and
green points.} \label{fig:correlation_parameters}   
\end{figure*}

@@

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. These models they have another particular
  feature: their minimum mass is exactly $M_{\rm min}=10^{10.9}\hMsun$
  and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$
  close to $1.0$ (instead of the observational value of $0.8$) and
  $\theta_0$ on the range of $13^{\prime}$ (the mean observational
  value is close to $8^{\prime}$) but are considered consistent
  because their large error bars barely overlap with the observational
  expectation (see figure \ref{fig:correlation_parameters}).
  Because these models are are barely compatible with observations and
  are a minority of the consistent models, we exclude them from the
  discussion.}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
\end{center}
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right) planes showing the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function from \citet{Ouchi2008,Ouchi2010}.   
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

\subsection{Two relevant features in the preferred models}
There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$, {\bf half of them $\Delta M\leq 0.5$}.
